---
title: "QMM_Final"
author: "Krupa, Niharika, Vivek"
date: "2023-12-06"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Problem Statement**

We have been asked to assign 15 students to a group project. 

Division: The 15 students has been put into five different groups which means each group has 3 students.

We have determined that attendance, experience and GPA are the three main criteria that have a big impact on how well groups complete the project. To get the best results possible on the class project, each of these elements is essential.

**Generating the data**

1) Attendance

```{r}
set.seed(1)
Attendance <- round(runif(15, min = 0, max = 30))
print(Attendance)
Mean_A <- round(weighted.mean(Attendance))
Mean_A
```


2) Experience

```{r}
set.seed(2)
Experience <- round(runif(15, min = 0, max = 100))
print(Experience)
Mean_E <- round(weighted.mean(Experience))
Mean_E
```

3) GPA PERCENTAGE

```{r}
set.seed(3)
GPA <- round(runif(15, min = 0, max = 100))
print(GPA)
Mean_G <- round(weighted.mean(GPA))
Mean_G
```

**Creating data frame**

```{r}
data <- data.frame(student=1:15,Attendance, Experience, GPA)
data

Average <- rowMeans(data[, c("Attendance", "Experience", "GPA")])
round(Average)

data$Average <- round(Average)
data
```


*Creating the table of students along with the factors and their values*
```{r}
table <- matrix(c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,
                  8,11,17,27,6,27,28,20,19,2,6,5,21,12,23,
                  18,70,57,17,94,94,13,83,47,55,55,24,76,18,41,
                  17,81,38,33,60,60,12,29,58,63,51,51,53,56,87,
                  14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50),ncol = 5,byrow = F)

colnames(table) <- c("Student_No","Attendance","Experience","GPA","Average")
rownames(table) <- c(1:15)

as.table(table)
```

**Mathematical formulation**

Objective function:

$$ \sum_{i=1}^{15}\sum_{j=1}^5 (F_{1i}+ F_{2i} +F_{3i})/3*X_{ij}, where \: i = 1, 2, 3, 4,5.......,15 \: and  \: j = 1,2,3,4,5$$


**constraints**

**Student constraint**

Each student is assigned to exactly one group.

$$ \sum_{j=1}^{5}\ X_{ij} = 1, ∀i $$

**Group constraint**

Each group should have exactly 3 members.

$$ \sum_{i=1}^{15}\ g_{ij} = 3, ∀j $$

**Non-Negativity constraint**

$$Xij ≥ 0,∀i,j$$


**Factor constraints**

**Attendance constraint**

The number of hours group members are attending the meetings scheduled for the project.

$$ \sum_{j=1}^{15}Attendace_{j}*X_{ij}  \geq Avg(Attendance), where \: i = 1, 2, 3, 4,5 \: and  \: j = 1,2,3,4, 5, ... , 15, ∀i,j$$

**Experience constraint**

Experience in the related field, their experience is rated from 0 to 100. 1 being the lowest and 10 being the highest.

$$ \sum_{j=1}^{15}Experience_{j}*x_{ij}  \geq Avg(Experience), where \: i = 1, 2, 3, 4, 5 \: and  \: j = 1,2,3,4, 5, ... , 15, ∀i,j$$

**GPA constraint**

The students have been scaled on a percentage from 0 to 100 where 0%  being given to the student with least overall grade and 100% to students with the highest overall grade.

$$ \sum_{j=1}^{15}GPA_{j}*x_{ij}  \geq Avg(GPA), where \: i = 1, 2, 3, 4, 5 \: and  \: j = 1,2,3,4, 5, ... , 15, ∀i,j$$


**Mathematical formulation of the constraints**

**Objective function**

$$MaxZ= 14g1x1 + 54g1x2 + 37g1x3 + 26g1x4 + 53g1x5 + 60g1x6 + 18g1x7 + 44g1x8 + 41g1x9 + 40g1x10 +  37g1x11 + 27g1x12 + 50g1x13 + 29g1x14 + 50g1x15 +
14g2x1 + 54g2x2 + 37g2x3 + 26g2x4 + 53g2x5 + 60g2x6 + 18g2x7 + 44g2x8 + 41g2x9 + 40g2x10 +  37g2x11 + 27g2x12 + 50g2x13 + 29g2x14 + 50g2x15 +
14g3x1 + 54g3x2 + 37g3x3 + 26g3x4 + 53g3x5 + 60g3x6 + 18g3x7 + 44g3x8 + 41g3x9 + 40g3x10 +  37g3x11 + 27g3x12 + 50g3x13 + 29g3x14 + 50g3x15 +
14g4x1 + 54g4x2 + 37g4x3 + 26g4x4 + 53g4x5 + 60g4x6 + 18g4x7 + 44g4x8 + 41g4x9 + 40g4x10 +  37g4x11 + 27g4x12 + 50g4x13 + 29g4x14 + 50g4x15 +
14g5x1 + 54g5x2 + 37g5x3 + 26g5x4 + 53g5x5 + 60g5x6 + 18g5x7 + 44g5x8 + 41g5x9 + 40g5x10 +  37g5x11 + 27g5x12 + 50g5x13 + 29g5x14 + 50g5x15$$

where "g" is group ranging from 1 to 5 and "x" is students ranging from 1 to 15


**constraint**

**Group constraint**

$$Group 1: g1x1 + g1x2 + g1x3 + g1x4 + g1x5 + g1x6 + g1x7 + g1x8 + g1x9 + g1x10 + g1x11 + g1x12 + g1x13 + g1x14 + g1x15 = 3$$

$$Group2: g2x1 + g2x2 + g2x3 + g2x4 + g2x5 + g2x6 + g2x7 + g2x8 + g2x9 + g2x10 + g2x11 + g2x12 + g2x13 + g2x14 + g2x15 = 3$$

$$Group3: g3x1 + g3g2 + g3x3 + g3x4 + g3x5 + g3x6 + g3x7 + g3x8 + g3x9 + g3x10 + g3x11 + g3x12 + g3x13 + g3x14 + g3x15 = 3$$

$$Group4: g4x1 + g4g2 + g4x3 + g4x4 + g4x5 + g4x6 + g4x7 + g4x8 + g4x9 + g4x10 + g4x11 + g4x12 + g4x13 + g4x14 + g4x15 = 3$$

$$Group5: g5x1 + g5g2 + g5x3 + g5x4 + g5x5 + g5x6 + g5x7 + g5x8 + g5x9 + g5x10 + g5x11 + g5x12 + g5x13 + g5x14 + g5x15 = 3$$


**Attendance constraint**

For group 1: 8g1x1 + 11g1x2 + 17g1x3 + 27g1x4 + 6g1x5 + 27g1x6 + 28g1x7 + 20g1x8 + 19g1x9 + 2g1x10 +  6g1x11 + 5g1x12 + 21g1x13 + 12g1x14 + 23g1x15 >=15

For group 2: 8g2x1 + 11g2x2 + 17g2x3 + 27g2x4 + 6g2x5 + 27g2x6 + 28g2x7 + 20g2x8 + 19g2x9 + 2g2x10 +  6g2x11 + 5g2x12 + 21g2x13 + 12g2x14 + 23g2x15 >=15

For Group 3: 8g3x1 + 11g3x2 + 17g3x3 + 27g3x4 + 6g3x5 + 27g3x6 + 28g3x7 + 20g3x8 + 19g3x9 + 2g3x10 +  6g3x11 + 5g3x12 + 21g3x13 + 12g3x14 + 23g3x15 >=15

For Group 4: 8g4x1 + 11g4x2 + 17g4x3 + 27g4x4 + 6g4x5 + 27g4x6 + 28g4x7 + 20g4x8 + 19g4x9 + 2g4x10 +  6g4x11 + 5g4x12 + 21g4x13 + 12g4x14 + 23g4x15 >=15

For Group 5: 8g5x1 + 11g5x2 + 17g5x3 + 27g5x4 + 6g5x5 + 27g5x6 + 28g5x7 + 20g5x8 + 19g5x9 + 2g5x10 +  6g5x11 + 5g5x12 + 21g5x13 + 12g5x14 + 23g5x15 >=15


**Experience constraint**

For Group 1: 18g1x1 + 70g1x2 + 57g1x3 + 17g1x4 + 94g1x5 + 94g1x6 + 13g1x7 + 83g1x8 + 47g1x9 + 55g1x10 +  55g1x11 + 24g1x12 + 76g1x13 + 18g1x14 + 41g1x15 >=51

For Group 2: 18g2x1 + 70g2x2 + 57g2x3 + 17g2x4 + 94g2x5 + 94g2x6 + 13g2x7 + 83g2x8 + 47g2x9 + 55g2x10 +  55g2x11 + 24g2x12 + 76g2x13 + 18g2x14 + 41g2x15 >=51

For group 3: 18g3x1 + 70g3x2 + 57g3x3 + 17g3x4 + 94g3x5 + 94g3x6 + 13g3x7 + 83g3x8 + 47g3x9 + 55g3x10 +  55g3x11 + 24g3x12 + 76g3x13 + 18g3x14 + 41g3x15 >=51

For group 4: 18g4x1 + 70g4x2 + 57g4x3 + 17g4x4 + 94g4x5 + 94g4x6 + 13g4x7 + 83g4x8 + 47g4x9 + 55g4x10 +  55g4x11 + 24g4x12 + 76g4x13 + 18g4x14 + 41g4x15 >=51

For group 5: 18g5x1 + 70g5x2 + 57g5x3 + 17g5x4 + 94g5x5 + 94g5x6 + 13g5x7 + 83g5x8 + 47g5x9 + 55g5x10 +  55g5x11 + 24g5x12 + 76g5x13 + 18g5x14 + 41g5x15 >=51


**GPA constraint**

For Group 1: 17g1x1 + 81g1x2 + 38g1x3 + 33g1x4 + 60g1x5 + 60g1x6 + 12g1x7 + 29g1x8 + 58g1x9 + 63g1x10 +  51g1x11 + 51g1x12 + 53g1x13 + 56g1x14 + 87g1x15 >=50

For Group 2: 17g2x1 + 81g2x2 + 38g2x3 + 33g2x4 + 60g2x5 + 60g2x6 + 12g2x7 + 29g2x8 + 58g2x9 + 63g2x10 +  51g2x11 + 51g2x12 + 53g2x13 + 56g2x14 + 87g2x15 >=50

For Group 3: 17g3x1 + 81g3x2 + 38g3x3 + 33g3x4 + 60g3x5 + 60g3x6 + 12g3x7 + 29g3x8 + 58g3x9 + 63g3x10 +  51g3x11 + 51g3x12 + 53g3x13 + 56g3x14 + 87g3x15 >=50

For Group 4: 17g4x1 + 81g4x2 + 38g4x3 + 33g4x4 + 60g4x5 + 60g4x6 + 12g4x7 + 29g4x8 + 58g4x9 + 63g4x10 +  51g4x11 + 51g4x12 + 53g4x13 + 56g4x14 + 87g4x15 >=50

For Group 5: 17g5x1 + 81g5x2 + 38g5x3 + 33g5x4 + 60g5x5 + 60g5x6 + 12g5x7 + 29g5x8 + 58g5x9 + 63g5x10 +  51g5x11 + 51g5x12 + 53g5x13 + 56g5x14 + 87g5x15 >=50


**Individual constraint**

1. g1x1+g2x1+g3x1+g4x1+g5x1=1 

2. g1x2+g2x2+g3x2+g4x2+g5x2=1

3. g1x3+g2x3+g3x3+g4x3+g5x3=1

4. g1x4+g2x4+g3x4+g4x4+g5x4=1

5. g1x5+g2x5+g3x5+g4x5+g5x5=1

6. g1x6+g2x6+g3x6+g4x6+g5x6=1

7. g1x7+g2x7+g3x7+g4x7+g5x7=1

8. g1x8+g2x8+g3x8+g4x8+g5x8=1

9. g1x9+g2x9+g3x9+g4x9+g5x9=1

10. g1x10+g2x10+g3x10+g4x10+g5x10=1

11. g1x11+g2x11+g3x11+g4x11+g5x11=1

12. g1x12+g2x12+g3x12+g4x12+g5x12=1

13. g1x13+g2x13+g3x13+g4x13+g5x13=1

14. g1x14+g2x14+g3x14+g4x14+g5x14=1

15. g1x15+g2x15+g3x15+g4x15+g5x15=1

##Solving the problem in R.

### Loading required libraries.
```{r}
library(lpSolve)
library(lpSolveAPI)
```

### Gemerating a LP problem with both 35 constraints and 75 decision variables
```{r}
LP_model <- make.lp(35, 75)
LP_model
```

### LP_model is an object that represents the LP problem.

#This statement sets the cofficients for the objective functions seventy five decision variables. It provides a vector containing these coefficients, emphasizing the importance of maintaining a consistent order for both the variables in the objective function and the constraints.

```{r}
set.objfn(LP_model, c(14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50,
                      14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50,
                      14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50,
                      14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50,
                      14, 54, 37, 26, 53, 60, 18, 44, 41, 40, 37, 27, 50, 29, 50))
```

### By setting the objective sense to "max" this line's aim is to maximize the objective function.
```{r}
lp.control(LP_model, sense = 'max')
```

### Adding constraints to the LP problem.

```{r}
#Group 1
set.row(LP_model,1,c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

# Group 2
set.row(LP_model,2,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

# Group 3
set.row(LP_model,3,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

 # Group 4
set.row(LP_model,4,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))

# Group 5
set.row(LP_model,5,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)) 

#Attendance constraint for group 1
set.row(LP_model,6,c(8,11,17,27,6,27,28,20,19,2,6,5,21,12,23,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Attendance constraint for group 2
set.row(LP_model,7,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,8,11,17,27,6,27,28,20,19,2,6,5,21,12,23,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))

#Attendance constraint for group 3
set.row(LP_model,8,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,8,11,17,27,6,27,28,20,19,2,6,5,21,12,23,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))

#Attendance constraint for group 4
set.row(LP_model,9,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,8,11,17,27,6,27,28,20,19,2,6,5,21,12,23,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Attendance constraint for group 5
set.row(LP_model,10,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,8,11,17,27,6,27,28,20,19,2,6,5,21,12,23))

#Experience constraint for group 1
set.row(LP_model,11,c(18,70,57,17,94,94,13,83,47,55,55,24,76,18,41,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Experience constraint for group 2
set.row(LP_model,12,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,18,70,57,17,94,94,13,83,47,55,55,24,76,18,41,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Experience constraint for group 3
set.row(LP_model,13,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,18,70,57,17,94,94,13,83,47,55,55,24,76,18,41,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Experience constraint for group 4
set.row(LP_model,14,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,18,70,57,17,94,94,13,83,47,55,55,24,76,18,41,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Experience constraint for group 5
set.row(LP_model,15,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,18,70,57,17,94,94,13,83,47,55,55,24,76,18,41))

#GPA constraint for group 1
set.row(LP_model,16,c(17,81,38,33,60,60,12,29,58,63,51,51,53,56,87,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#GPA constraint for group 2
set.row(LP_model,17,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17,81,38,33,60,60,12,29,58,63,51,51,53,56,87,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0
)) 

#GPA constraint for group 3
set.row(LP_model,18,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17,81,38,33,60,60,12,29,58,63,51,51,53,56,87,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#GPA constraint for group 4
set.row(LP_model,19,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17,81,38,33,60,60,12,29,58,63,51,51,53,56,87,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0))

#GPA constraint for group 5
set.row(LP_model,20,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,17,81,38,33,60,60,12,29,58,63,51,51,53,56,87))

#Student 1 constraint
set.row(LP_model,21,c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Student 2 constraint
set.row(LP_model,22,c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Student 3 constraint
set.row(LP_model,23,c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0)) 

#Student 4 constraint
set.row(LP_model,24,c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0)) 

#Student 5 constraint
set.row(LP_model,25,c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0)) 

#Student 6 constraint
set.row(LP_model,26,c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0)) 

#Student 7 constraint
set.row(LP_model,27,c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0)) 

#Student 8 constraint
set.row(LP_model,28,c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0)) 

#Student 9 constraint
set.row(LP_model,29,c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0)) 

#Student 10 constraint
set.row(LP_model,30,c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0)) 

#Student 11 constraint
set.row(LP_model,31,c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0)) 

#Student 12 constraint
set.row(LP_model,32,c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0)) 

#Student 13 constraint
set.row(LP_model,33,c(0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0))

#Student 14 constraint
set.row(LP_model,34,c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0))

#Student 15 constraint
set.row(LP_model,35,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)) 
```

###Setting the right hand side values for the constraints in LP problem.
```{r}
rhs<-c(rep(3,5), rep(15,5), rep(51,5), rep(51,5), rep(1,15))
set.rhs(LP_model,rhs)
```

### Setting the directions(Types) and bounds to the LP problem.
```{r}
set.constr.type(LP_model,c(rep("=",5),rep(">=", 15), rep("=",15)))
set.bounds(LP_model,lower = rep(0,75))
```

### Setting the type to integer
```{r}
set.type(LP_model, 1:75 ,type = "integer") 
```


### Solving the Lp problem using the constraints and objective function.
```{r}
solve(LP_model)
```

### Getting the value of objective function.
```{r}
get.objective(LP_model)
```

### Getting the values of decision variables.
```{r}
round(get.variables(LP_model))
```

### Getting the values of constraints.
```{r}
get.constraints(LP_model)
```

